Finding Quality Issues in SKOS Vocabularies

### 2012-03-24 analysis.tex
added some more numeric values, resolved some todos

\textbf{Vocabulary} & \rotatebox{90}{\textbf{Abbrev.}} & \rotatebox{90}{\textbf{Version/last mod.}} & \rotatebox{90}{\textbf{Concepts}} & \rotatebox{90}{\textbf{Auth. Concepts}} & \rotatebox{90}{\textbf{Labels}} & \rotatebox{90}{\textbf{Semantic Rel.}} & \rotatebox{90}{\textbf{Aggregation Rel.}} & \rotatebox{90}{\textbf{Concept Schemes}} & \rotatebox{90}{\textbf{Collections}}\\
\toprule
Gemeenschappelijke Thesaurus Audiovisuele Archieven & \textbf{GTAA} & 2010/08/25 & 171991 && 178776 & 50892 & 343980 & 9 & 0 \\
\hline
Geonames Ontology & \textbf{Geonames} & 2.2.1 & 671 & 671 & 671 & 0 & 671 & 9 & 0 \\
\hline
Medical Subject Headings & \textbf{MeSH} & ? & 24626 & 24626 & 150617 & 38858 & 0 & 0 & 0 \\
\hline
Peroxisome Knowledge Base & \textbf{PXV} & 1.6 & 2112 & 1686 & 3628 & 2695 & 1716 & 1 & 0 \\
\hline
The EU's multilingual thesaurus & \textbf{Eurovoc} & 5.0 & 6797 && 457788 & 18491 & 15512 & 128 & 0 \\
\hline
Integrated Public Sector Vocabulary & \textbf{IPSV} & 2.00 & 4732 && 7945 & 13843 & 4483 & 3 & 0 \\
\hline
Agricultural Thesaurus & \textbf{AGROVOC} & 1.3 & 32035 && 620629 & 65934 & 32085 & 1 & 0 \\
\hline
DBpedia Categories & \textbf{DBPedia} & ? & 743410 && 740352 & 1490316 & 0 & 0 & 0 \\
\hline
University of Southampton Pressinfo & \textbf{Pressinfo} & 2011/02/24 & 1125 && 0 & 0 & 0 & 0 & 0 \\
\hline
New York Times People & \textbf{NYTP} & 2010/06/22 & 4979 && 4979 & 0 & 4979 & 1 & 0 \\
\hline
Library of Congress Subject Headings & \textbf{LCSH} & ? & 459182 && 746076 & 595754 & 815816 & 19 & 0 \\
\hline
Middle Kingdom tombs of Ancient Egypt Thesaurus & \textbf{Meketre} & 2011/07/07 & 422 && 569 & 1698 & 6 & 2 & 0 \\
\hline
Thesaurus for Economics & \textbf{STW} & 8.06 & 6524 && 31189 & 57907 & 6531 & 1 & 0 \\
\hline
North American Industry Classification System & \textbf{NAICS} & 2012 & 4175 && 0 & 8684 & 2235 & 1 & 0 \\
\hline
Austrian Armed Forces Thesaurus & \textbf{LVAk} & n/a & 13411 && 17250 & 16346 & 0 & 0 & 0 \\
\bottomrule
\end{tabular}

@@

Undocumented Concepts & 96850 & 0 & 1807 & 1918 & 5341 & 4551 & 32035 & 743410 & 1125 & 4094 & tba & 422 & 5236 & 3259 & 13411 \\

@@

Valueless Associative Relations & 9438 & 0 & 495 & 0 & 1 && 282 & 8120 & 0 & 0 & 1879 && 5082 & 0 & 5 \\

Solely Transitively Related Concepts & 0 & 0 & 0 & 0 & 2652 && 0 & 0 & 0 & 0 & 0 && 0 & 2189 & 0 \\

Omitted Top Concepts & 9 & 9 & 0 & 0 & 1 && 0 & 0 & 0 & 1 & 18 && 0 & 0 & 0 \\

Top Concept Having Broader Concepts & 0 & 0 & 0 & 1 & 0 && 0 & 0 & 0 & 0 & 0 && 0 & 0 & 0 \\

@@

Missing In-Links &&&&&&&&&&&&&&& 13411 \\

Missing Out-Links &&&&&&&&&&&&&&& 13411 \\

Broken Links & 0 & 0 & 1 & 99 &&& 238 & 0* & 11 & 7 && 425 & 1 & 3169 & n/a \\

@@

% Labeling and Documentation Issues
We found labeling and documentation issues in all analyzed vocabularies. PXV provides labels for XX\% of its concepts, Pressinfo labels only for 1 out of 1125 concepts, and the STW thesaurus misses labels for two concepts. Eurovoc and NAICS use SKOS-XL labels, which are currently not supported by qSKOS.
Incomplete Language Coverage were issues in the three analyzed vocabularies: in AGROVOC all concepts had incomplete coverage, probably because \todo{CM}{why?}, and in STW we found XX\%.
Most vocabularies didn't document their concepts with the documentary properties defined by SKOS.
Label conflicts, hence \todo{CM}{explain briefly} were found in several vocabularies: GTAA has many because? PXV has 7. Why given examples?

>>>>

\textbf{Vocabulary} & \rotatebox{90}{\textbf{Abbrev.}} & \rotatebox{90}{\textbf{Version/last mod.}} & \rotatebox{90}{\textbf{Concepts}} & \rotatebox{90}{\textbf{Auth. Concepts}} & \rotatebox{90}{\textbf{Labels}} & \rotatebox{90}{\textbf{Semantic Rel.}} & \rotatebox{90}{\textbf{Aggregation Rel.}} & \rotatebox{90}{\textbf{Concept Schemes}} & \rotatebox{90}{\textbf{Collections}}\\
\toprule
Gemeenschappelijke Thesaurus Audiovisuele Archieven & \textbf{GTAA} & 2010/08/25 & 171991 & 171991 & 178776 & 50892 & 343980 & 9 & 0 \\
\hline
Geonames Ontology & \textbf{Geonames} & 2.2.1 & 671 & 671 & 671 & 0 & 671 & 9 & 0 \\
\hline
Medical Subject Headings & \textbf{MeSH} & ? & 24626 & 24626 & 150617 & 38858 & 0 & 0 & 0 \\
\hline
Peroxisome Knowledge Base & \textbf{PXV} & 1.6 & 2112 & 1686 & 3628 & 2695 & 1716 & 1 & 0 \\
\hline
The EU's multilingual thesaurus & \textbf{Eurovoc} & 5.0 & 6797 && 457788 & 18491 & 15512 & 128 & 0 \\
\hline
Integrated Public Sector Vocabulary & \textbf{IPSV} & 2.00 & 4732 && 7945 & 13843 & 4483 & 3 & 0 \\
\hline
Agricultural Thesaurus & \textbf{AGROVOC} & 1.3 & 32035 && 620629 & 65934 & 32085 & 1 & 0 \\
\hline
DBpedia Categories & \textbf{DBPedia} & ? & 743410 && 740352 & 1490316 & 0 & 0 & 0 \\
\hline
University of Southampton Pressinfo & \textbf{Pressinfo} & 2011/02/24 & 1125 & 1125 & 0 & 0 & 0 & 0 & 0 \\
\hline
New York Times People & \textbf{NYTP} & 2010/06/22 & 4979 & 4979 & 4979 & 0 & 4979 & 1 & 0 \\
\hline
Library of Congress Subject Headings & \textbf{LCSH} & 2011/08/09 & 459182 & 407908 & 746076 & 595754 & 815816 & 19 & 0 \\
\hline
Middle Kingdom tombs of Ancient Egypt Thesaurus & \textbf{Meketre} & 2011/07/07 & 422 & 422 & 569 & 1698 & 6 & 2 & 0 \\
\hline
Thesaurus for Economics & \textbf{STW} & 8.06 & 6524 && 31189 & 57907 & 6531 & 1 & 0 \\
\hline
North American Industry Classification System & \textbf{NAICS} & 2012 & 4175 && 0 & 8684 & 2235 & 1 & 0 \\
\hline
Austrian Armed Forces Thesaurus & \textbf{LVAk} & n/a & 13411 && 17250 & 16346 & 0 & 0 & 0 \\
\bottomrule
\end{tabular}

@@

Undocumented Concepts & 96850 & 0 & 1807 & 1918 & 5341 & 4551 & 32035 & 743410 & 1125 & 4094 & 398036 & 422 & 5236 & 3259 & 13411 \\

@@

Valueless Associative Relations & 9438 & 0 & 495 & 0 & 1 && 282 & 8120 & 0 & 0 & 1879 & 0 & 5082 & 0 & 5 \\

Solely Transitively Related Concepts & 0 & 0 & 0 & 0 & 2652 && 0 & 0 & 0 & 0 & 0 & 36 & 0 & 2189 & 0 \\

Omitted Top Concepts & 9 & 9 & 0 & 0 & 1 && 0 & 0 & 0 & 1 & 18 & 0 & 0 & 0 & 0 \\

Top Concept Having Broader Concepts & 0 & 0 & 0 & 1 & 0 && 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\

@@

Missing In-Links && 19 && 1686 &&&&& 1125 & 20 && 422 & 6516 & 2213 & 13411 \\

Missing Out-Links && 671 && 1472 &&&&& 1116 & 0 && 273 & 6524 & 0 & 13411 \\

Broken Links & 0 & 0 & 1 & 163 &&& 238 & 0* & 11 & 7 && 425 & 1 & 3169 & n/a \\

@@

% Labeling and Documentation Issues
We found labeling and documentation issues in all analyzed vocabularies. PXV provides labels for XX\% of its concepts, Pressinfo labels only for 1 out of 1125 concepts, and the STW thesaurus misses labels for two concepts. Eurovoc and NAICS use SKOS-XL labels, which are currently not supported by qSKOS.
Incomplete Language Coverage were issues in the three analyzed vocabularies: in AGROVOC all concepts had incomplete coverage, probably because \todo{CM}{es gibt labels in insgesamt 25 versch sprachen und keines der konzepte ist in jeder sprache beschrieben}, and in STW we found XX\%.
Most vocabularies didn't document their concepts with the documentary properties defined by SKOS.
Label conflicts, hence \todo{CM}{explain briefly} were found in several vocabularies: GTAA has many because? PXV has 7. Why given examples?

### 2012-03-24 related_work.tex
added some more numeric values, resolved some todos

Ontology evaluation is task of measuring the quality of an ontology and has extensively been discussed by Vrandecic~[\todo{CM}{ref denny}]. Gangemi [\todo{CM}{ref ?}] introduced structural, functional and usability-related measures for ontology evaluation, Arpinar [\todo{CM}{ref ?}] define three types of conflicts that may occur in ontologies, and also Tartir et al.[\todo{CM}{ref ?}] propose a framework for evaluation and ranking of ontologies. Although there are definitely overlaps between ontology evaluation and our research, the quality issues we identified are less tight to underlying data model and formal ontology definition language but, to a large extent, derived from manuals and guidelines taxonomist use in their daily work.

>>>>

Ontology evaluation is task of measuring the quality of an ontology and has extensively been discussed by Vrandecic~\cite{Vrandecic2010}. Gangemi~\cite{Gangemi2006} introduced structural, functional and usability-related measures for ontology evaluation, Arpinar~\cite{Arpinar2006} define three types of conflicts that may occur in ontologies, and also Tartir et al.~\cite{Tartir2007} propose a framework for evaluation and ranking of ontologies. Although there are definitely overlaps between ontology evaluation and our research, the quality issues we identified are less tight to underlying data model and formal ontology definition language but, to a large extent, derived from manuals and guidelines taxonomist use in their daily work.
